### 2018-09-27 paper.tex
Wip

  We present Guild AI, an open source toolkit that facilitates model
  reuse for application development by applying traditional software
  packaging constructs to the domain of machine learning. Package
  management strategies are central to successful software
  ecosystems. Examples include \href{https://www.npmjs.com/}{npm} for
  JavaScript, \href{https://wiki.debian.org/Apt}{APT} for Debian, and
  \href{https://pip.pypa.io}{pip} for Python. While such tools excel
  at creating traditional software packages, machine learning
  applications present unique requirements that call for
  specialization. Guild AI combines the proven effectiveness of
  package managers with novel features to enable machine learning
  model reuse for application development across a variety of use
  cases.

@@

@@

@@

@@

@@

\subsection{Starging a Run}

@@

\subsection{Requires Resource Resolution}

@@

@@

@@

>>>>

  We present Guild AI, an open source toolkit that facilitates model
  reuse for application development by applying traditional software
  packaging constructs to the domain of machine learning. Package
  management strategies are central to successful software
  ecosystems. Examples include \href{https://www.npmjs.com/}{npm} for
  JavaScript, \href{https://wiki.debian.org/Apt}{APT} for Debian, and
  \href{https://pip.pypa.io}{pip} for Python. Such tools excel at
  creating traditional software packages. However, machine learning
  applications present unique requirements that call for tool
  specialization. Guild AI combines the proven effectiveness of
  package managers with novel features to enable machine learning
  model reuse for application development across a variety of use
  cases.

@@

Code reuse is a central tenet in software development and is supported
by myriad techniques, abstractions, and tools. Effective code reuse
allows developers to leverage prior work in a consistent, reliable
manner that saves time and improves software quality. In this paper we
consider code reuse in terms of \emph{packaged software} in the
context of machine learning.

\subsection{Traditional packaged software}

Packaged software is software that is organized in a way that can be
easily installed and used by \emph{users}. A user is a consumer of
software, rather than a producer or developer. A user may be software
developer, in the case of consuming software libraries or frameworks,
or she may be an end-user who uses software as a program using a
graphical or command line interface. In both cases, packaged software
may be provided in units that the user can install and start using
quickly and reliably.

This is an example of installing packaged software:

{\footnotesize
\begin{verbatim}
 $ pip install tensorflow
\end{verbatim}}

By running this command, a user is using a \emph{package manager}---in
this case the program \verb|pip|---to install a package named
\verb|tensorflow|. With this innocuous command, the user implicitly expects
a number of things:

\begin{itemize}
\item The Python module \verb|tensorflow| should be installed
\item Additional Python modules required by \verb|tensorflow| should
  also be installed
\item Installed software should work as expected on the target system
\item At a future date \verb|tensorflow| may be similarly uninstalled along
  with its no-longer-needed required packages
\item The act of installing and uninstalling \verb|tensorflow| should
  not break or otherwise destabilize other installed software on the
  target system
\end{itemize}

Such a package management facilities are essential to code reuse at
the system level. Package managers allow users to consume and manage
complex software systems with simple commands in a way that maintains
the integrity of other installed software. They support rapid
experimentation with new software as users are free to install, use,
and evaluate packages with the confidence that they can safely remove
that software later.

Package managers promote healthy software ecosystems by facilitating
software \emph{publishing}. Software authors use packaging tools to
create the installable software units---\emph{packages}---that are so
easily consumed by users. By publishing packaged software, developers
signify that their software will work as advertised if installed using
the supported tools.

Immense software ecosystems that are enabled by package managers
include Python, JavaScript, Ruby, Go, and R. The GNU/Linux operating
system itself is an ecosystem of package management ecosystems
including packaging schemes from Debian, RedHat, Gentoo, and Arch
distributions. Package managers are established cornerstones of
software reuse across languages and operating systems.

\subsection{Code reuse and machine learning models}

A \emph{machine learning model} is challenging to define as models
have different contexts. In the most general context, models are
mathematical concepts or language that represents a system
(needref). In the context of machine learning, models may be
represented by computer source code, either explicitly as declared
structures, or implicitly by way of executable instructions that
perform model related tasks. A \emph{trained model} is a model that
has learned some representation of a system through the process of
computer based optimization.

For the purpose of our discussion, a machine learning model is a
software representation of a specific mathetical concept that can be
trained by a computer. Models may be in various states:
\emph{uninitialized}, \emph{initialized}, \emph{partially trained},
\emph{fully trained}. Regardless of state, the distinguishing feature
of machine learning models for our purpose is that they support
runnable computer operations.

Models---and in particular \emph{trained models}--- are similar to
traditional software in that they can be executed to perform
computations. In fact, the purpose of training a model is to create a
computer program. The difference between a trained model and a human
authored program is one of method: a trained model is learned by an
algorithm while a human authored program is written manually.

@@

Need to define reuse. Start with traditional softwar reuse and make it
clear that Guild addresses model reuse. What is model reuse?

@@

Apply analogy of system packaging and the importance of formalizing
the process with protocols and reference implementations.

@@

- Packaging tools

@@

\subsection{Starting a Run}

@@

\subsection{Resource Resolution}

\subsection{Model Testing}

\subsection{Packaging and Distribution}

@@

- Workshops
- User feedback

@@

- slim, object-detection, mnist, hello

@@

\section{Summary}
